A Parallel, Backjumping Subgraph Isomorphism Algorithm using Supplemental Graphs

### 2015-06-22 paper/paper.tex
Tweak URL

Our algorithm was implemented\footnote{source code is available at
\url{https://github.com/ciaranm/parasols}} in C++ using C++11 native threads, and was compiled using
GCC 4.9.0.  We performed our experiments on a machine with dual Intel Xeon E5-2640 v2 processors
(for a total of 16 cores, and 32 hardware threads via hyper-threading), running Scientific Linux
6.6.  For the comparison with SND in the following section, we used Java HotSpot 1.8.0\_11. Runtimes
include preprocessing and thread launch costs, but not the time taken to read in the graph files
from disk (except in the case of SND, which we were unable to instrument).

>>>>

Our algorithm was implemented\footnote{source code, data and experimental scripts available at\\
\url{https://github.com/ciaranm/cp2015-subgraph-isomorphism}}in C++ using C++11 native threads, and
was compiled using GCC 4.9.0.  We performed our experiments on a machine with dual Intel Xeon
E5-2640 v2 processors (for a total of 16 cores, and 32 hardware threads via hyper-threading),
running Scientific Linux 6.6.  For the comparison with SND in the following section, we used Java
HotSpot 1.8.0\_11. Runtimes include preprocessing and thread launch costs, but not the time taken to
read in the graph files from disk (except in the case of SND, which we were unable to instrument).
